---
title: "Figure 6. Indica-enriched SynCom have stronger ability to promote rice growth under the supply of organic nitrogen than japonica-enriched SynCom."
author: "Yong-Xin Liu"
date: "2019/2/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clean workspace
rm(list=ls()) 
# Load setting and functions
source("../script/stat_plot_functions.R")
# Set output directory
output_dir="./"
```

IR24 rice plants were grown under inorganic nitrogen and organic nitrogen conditions (a mixture of 5 amino acids, Supplementary Table 12) with and without synthetic bacterial communities, including indica-enriched bacteria, japonica-enriched bacteria, soil-enriched bacteria, and corresponding heated killed bacteria as controls, respectively (Supplementary Table 12). After 2-week bacterial inoculation, rice plants are measured by root length (a), plant height (b), and shoot fresh weight (c). Boxplot shows combined data from three independent inoculation experiments with 3-5 technical replicates each (Supplementary Table 13). Different letters indicate significantly different groups (P < 0.05, ANOVA, Tukey-HSD). The horizontal bars within boxes represent medians. The tops and bottoms of boxes represent 75th and 25th quartiles, respectively. The upper and lower whiskers extend 1.5 × the interquartile range from the upper edge and lower edge of the box, respectively.


```{r}
group_list = c("GfIn", "GfOr", "IeOr", "JeOr", "SeOr", "IedOr", "JedOr", "SedOr")
A50 = paste0("A50", group_list)
IR24 = paste0("Ir24", group_list)

# A50 IR24
variety = "Ir24"
```


## a. Root Length

```{r RootLength, eval=TRUE, include=TRUE}
m="RootLength"
# read raw data"RootLength"
df = read.table("Sycom.txt", header=T, row.names=1, sep="\t")

# boxplot parameter 
index = df
index$group = index$GroupID
# colnames(df)

# data filter
index = index[,c("group", m)]
index = na.omit(index)

index=subset(index, group %in% IR24)
index$group = factor(index$group, levels = IR24)
# boxplot stat code
model = aov(index[[m]] ~ group, data=index)
Tukey_HSD = TukeyHSD(model, ordered = TRUE, conf.level = 0.95)
Tukey_HSD_table = as.data.frame(Tukey_HSD$group) 
write.table(paste(m, "\n\t", sep=""), file=paste(output_dir, variety, m,  ".txt",sep=""),append = F, quote = F, eol = "", row.names = F, col.names = F)
suppressWarnings(write.table(Tukey_HSD_table, file=paste(output_dir,variety,m,".txt",sep=""), append = T, quote = F, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = T, col.names = T))

out = LSD.test(model,"group", p.adj="none") # alternative fdr
stat = out$groups
index$stat=stat[as.character(index$group),]$groups
max=max(index[,c(m)])
min=min(index[,c(m)])
x = index[,c("group",m)]
y = x %>% group_by(group) %>% summarise_(Max=paste('max(',m,')',sep=""))
y=as.data.frame(y)
rownames(y)=y$group
index$y=y[as.character(index$group),]$Max + (max-min)*0.05

p = ggplot(index, aes(x=group, y=index[[m]], color=group)) +
	geom_boxplot(alpha=1, outlier.size=0, size=0.7, width=0.5, fill="transparent") +
	labs(x="Groups", y=paste(m, "")) + theme_classic() + main_theme +
	geom_text(data=index, aes(x=group, y=y, color=group, label= stat)) +
	geom_jitter( position=position_jitter(0.17), size=1, alpha=0.7)+theme(legend.position="none")
if (length(unique(index$group))>3){	p=p+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))}
ggsave(paste(output_dir, variety,m, ".pdf", sep=""), p, width = 5, height = 2.5)
p
```


## b. PlantHeight

```{r PlantHeight, eval=TRUE, include=TRUE}
m="PlantHeight"
df = read.table("Sycom.txt", header=T, row.names=1, sep="\t")

# boxplot parameter 
index = df
index$group = index$GroupID
# colnames(df)

# data filter
index = index[,c("group", m)]
index = na.omit(index)

index=subset(index, group %in% IR24)
index$group = factor(index$group, levels = IR24)
# boxplot stat code
model = aov(index[[m]] ~ group, data=index)
Tukey_HSD = TukeyHSD(model, ordered = TRUE, conf.level = 0.95)
Tukey_HSD_table = as.data.frame(Tukey_HSD$group) 
write.table(paste(m, "\n\t", sep=""), file=paste(output_dir, variety, m,  ".txt",sep=""),append = F, quote = F, eol = "", row.names = F, col.names = F)
suppressWarnings(write.table(Tukey_HSD_table, file=paste(output_dir,variety,m,".txt",sep=""), append = T, quote = F, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = T, col.names = T))

out = LSD.test(model,"group", p.adj="none") # alternative fdr
stat = out$groups
index$stat=stat[as.character(index$group),]$groups
max=max(index[,c(m)])
min=min(index[,c(m)])
x = index[,c("group",m)]
y = x %>% group_by(group) %>% summarise_(Max=paste('max(',m,')',sep=""))
y=as.data.frame(y)
rownames(y)=y$group
index$y=y[as.character(index$group),]$Max + (max-min)*0.05

p = ggplot(index, aes(x=group, y=index[[m]], color=group)) +
	geom_boxplot(alpha=1, outlier.size=0, size=0.7, width=0.5, fill="transparent") +
	labs(x="Groups", y=paste(m, "")) + theme_classic() + main_theme +
	geom_text(data=index, aes(x=group, y=y, color=group, label= stat)) +
	geom_jitter( position=position_jitter(0.17), size=1, alpha=0.7)+theme(legend.position="none")
if (length(unique(index$group))>3){	p=p+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))}
ggsave(paste(output_dir, variety,m, ".pdf", sep=""), p, width = 5, height = 2.5)
p
```


## c. Fresh Weight

```{r FreshWeight, eval=TRUE, include=TRUE}
m="FreshWeight"
df = read.table("Sycom.txt", header=T, row.names=1, sep="\t")

# boxplot parameter 
index = df
index$group = index$GroupID
# colnames(df)

# data filter
index = index[,c("group", m)]
index = na.omit(index)

index=subset(index, group %in% IR24)
index$group = factor(index$group, levels = IR24)
# boxplot stat code
model = aov(index[[m]] ~ group, data=index)
Tukey_HSD = TukeyHSD(model, ordered = TRUE, conf.level = 0.95)
Tukey_HSD_table = as.data.frame(Tukey_HSD$group) 
write.table(paste(m, "\n\t", sep=""), file=paste(output_dir, variety, m,  ".txt",sep=""),append = F, quote = F, eol = "", row.names = F, col.names = F)
suppressWarnings(write.table(Tukey_HSD_table, file=paste(output_dir,variety,m,".txt",sep=""), append = T, quote = F, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = T, col.names = T))

out = LSD.test(model,"group", p.adj="none") # alternative fdr
stat = out$groups
index$stat=stat[as.character(index$group),]$groups
max=max(index[,c(m)])
min=min(index[,c(m)])
x = index[,c("group",m)]
y = x %>% group_by(group) %>% summarise_(Max=paste('max(',m,')',sep=""))
y=as.data.frame(y)
rownames(y)=y$group
index$y=y[as.character(index$group),]$Max + (max-min)*0.05

p = ggplot(index, aes(x=group, y=index[[m]], color=group)) +
	geom_boxplot(alpha=1, outlier.size=0, size=0.7, width=0.5, fill="transparent") +
	labs(x="Groups", y=paste(m, "")) + theme_classic() + main_theme +
	geom_text(data=index, aes(x=group, y=y, color=group, label= stat)) +
	geom_jitter( position=position_jitter(0.17), size=1, alpha=0.7)+theme(legend.position="none")
if (length(unique(index$group))>3){	p=p+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))}
ggsave(paste(output_dir, variety,m, ".pdf", sep=""), p, width = 5, height = 2.5)
p
```
