---
title: "Figure 1. Root microbiota of indica and japonica. "
author: "Yong-Xin Liu"
date: "2019/2/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clean workspace
rm(list=ls()) 
# Load setting and functions
source("../script/stat_plot_functions.R")
# Set output directory
output_dir="./"
```


## a. World map

(a) Diagram of original collection sites (44 countries) of indica (red) and japonica (blue) rice. 

```{r geomap, echo=TRUE}
library(dplyr)
library(maptools)
library(ggplot2)
library(maps)

geotable = read.table("varieties_geo.txt", header = T, sep = "\t")
worldmap = map_data("world")

fig1 = ggplot(geotable, aes(Longitude, Latitude, color = Subspecies)) +
  geom_polygon(data = worldmap, aes(x = long, y = lat, group = group, fill = NA), color = "grey70", size = 0.25)+
  geom_point(size = 2.5, alpha = 0.5)+  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1")+  
  coord_cartesian()+
  scale_y_continuous(breaks = (-3:3)*30)+
  scale_x_continuous(breaks = (-6:6)*30)+
  labs(x="Longitude", y="Latitude", colour = "Subspecies" ) +
  theme_tufte()
ggsave(paste0(output_dir, "minicore-worldmap.pdf", sep=""), fig1, width = 9, height = 5)
fig1
```


## b. Experiment design

(b) Diagram of the experimental design for rice field trials. The indica and japonica varieties were arranged randomly. Harvested samples for each variety were surrounded by protection plants that separated the different varieties.

This figure is manually drawn by Adobe Illustrator.


## c. PCoA filed I

(c) Unconstrained Principal Coordinate Analysis with Bray-Curtis distance showing that the root microbiota of indica is separate from that of japonica in field I in the first axis (P < 0.001, PERMANOVA by Adonis). Ellipses cover 68% of the data for each rice subspecies.

```{r pcoa1}
design = read.table("../data/design.txt", header=T, row.names=1, sep="\t")
design$group=design$groupID

if (TRUE){
	sub_design = subset(design, group %in% c("LIND","LTEJ"))
	sub_design$group  = factor(sub_design$group, levels=c("LIND","LTEJ"))
}else{
	sub_design = design
}

# method = c("weighted_unifrac","unweighted_unifrac","bray_curtis")
# for(m in method){
m = "bray_curtis"
beta = read.table(paste(m,".txt",sep=""), header=T, row.names=1, sep="\t", comment.char="") 
idx = rownames(sub_design) %in% rownames(beta)
sub_design=sub_design[idx,]
sub_beta=beta[rownames(sub_design),rownames(sub_design)]
# k is dimension, 3 is recommended; eig is eigenvalues
pcoa = cmdscale(sub_beta, k=4, eig=T)
# get coordinate string, format to dataframme
points = as.data.frame(pcoa$points) 
eig = pcoa$eig
# rename group name
levels(sub_design$group)=c("indica","japonica")
points = cbind(points, sub_design$group)
colnames(points) = c("PC1", "PC2", "PC3", "PC4","group") 
p = ggplot(points, aes(x=PC1, y=PC2, color=group)) + geom_point(alpha=.7, size=2) +
	labs(x=paste("PCoA 1 (", format(100 * eig[1] / sum(eig), digits=4), "%)", sep=""),
	y=paste("PCoA 2 (", format(100 * eig[2] / sum(eig), digits=4), "%)", sep=""),
	title=paste(m," PCoA",sep="")) + theme_classic()
p = p + stat_ellipse(level=0.68)
ggsave(paste0(output_dir, "beta_filedI_", m, ".pdf", sep=""), p, width = 5, height = 3)
# }
p
```

## c. PCoA filed II

(d) Unconstrained Principal Coordinate Analysis with Bray-Curtis distance showing that the root microbiota of indica is separate from that of japonica in field II in the first axis (P < 0.001, PERMANOVA by Adonis).

```{r pcoa1}
design = read.table("../data/design.txt", header=T, row.names=1, sep="\t")
design$group=design$groupID

if (TRUE){
	sub_design = subset(design, group %in% c("HIND","HTEJ"))
	sub_design$group  = factor(sub_design$group, levels=c("HIND","HTEJ"))
}else{
	sub_design = design
}

# method = c("weighted_unifrac","unweighted_unifrac","bray_curtis")
# for(m in method){
m = "bray_curtis"
beta = read.table(paste(m,".txt",sep=""), header=T, row.names=1, sep="\t", comment.char="") 
idx = rownames(sub_design) %in% rownames(beta)
sub_design=sub_design[idx,]
sub_beta=beta[rownames(sub_design),rownames(sub_design)]
# k is dimension, 3 is recommended; eig is eigenvalues
pcoa = cmdscale(sub_beta, k=4, eig=T)
# get coordinate string, format to dataframme
points = as.data.frame(pcoa$points) 
eig = pcoa$eig
# rename group name
levels(sub_design$group)=c("indica","japonica")
points = cbind(points, sub_design$group)
colnames(points) = c("PC1", "PC2", "PC3", "PC4","group") 
p = ggplot(points, aes(x=PC1, y=PC2, color=group)) + geom_point(alpha=.7, size=2) +
	labs(x=paste("PCoA 1 (", format(100 * eig[1] / sum(eig), digits=4), "%)", sep=""),
	y=paste("PCoA 2 (", format(100 * eig[2] / sum(eig), digits=4), "%)", sep=""),
	title=paste(m," PCoA",sep="")) + theme_classic()
p = p + stat_ellipse(level=0.68)
ggsave(paste0(output_dir, "beta_filedII_", m, ".pdf", sep=""), p, width = 5, height = 3)
# }
p
```

## 1.E Boxplot show Alpha diversity

(E) Shannon index of the microbiome of roots from indica, japonica, and the corresponding bulk soil in two fields. Bulk soil shows the highest microbiome diversity. The root microbiome of indica shows a significantly higher Shannon index than that of japonica in both fields.
 
Plotting Alpha boxlot for field I & II

```{r alpha_boxplot, echo=TRUE}
# Read usearch alpha file
alpha = read.table("/mnt/bai/yongxin/rice/xianGeng/result/alpha/index.txt", header=T, row.names=1, sep="\t", comment.char="") 

# Read design
design = read.table("/mnt/bai/yongxin/rice/xianGeng/doc/design.txt", header=T, row.names=1, sep="\t")
# Uniform group column as group
design$group=design$groupID

# Select by manual set group
if (TRUE){
	sub_design = subset(design, group %in% c("LTEJ","LIND","LSoil1","HTEJ","HIND","HSoil1"))
# Set group order
	sub_design$group  = factor(sub_design$group, levels=c("LTEJ","LIND","LSoil1","HTEJ","HIND","HSoil1"))
}else{
	sub_design = design
}

# Cross filter
idx = rownames(sub_design) %in% rownames(alpha)
sub_design=sub_design[idx,]
sub_alpha=alpha[rownames(sub_design),]

# Add design to alpha
index = cbind(sub_alpha, sub_design) 


# sub_function. loop for statiscs and plot for each index
method = c("chao1","richness","shannon_e")
# for(m in method){
  m = "shannon_e"
	model = aov(index[[m]] ~ group, data=index)
	Tukey_HSD = TukeyHSD(model, ordered = TRUE, conf.level = 0.95)
	Tukey_HSD_table = as.data.frame(Tukey_HSD$group) 
	write.table(paste(m, "\n\t", sep=""), file=paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/alpha_",m,".txt",sep=""),append = F, quote = F, eol = "", row.names = F, col.names = F)
	suppressWarnings(write.table(Tukey_HSD_table, file=paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/alpha_",m,".txt",sep=""), append = T, quote = F, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = T, col.names = T))

	# LSD test
	out = LSD.test(model,"group", p.adj="none") # alternative fdr
	stat = out$groups
	index$stat=stat[as.character(index$group),]$groups
	max=max(index[,c(m)])
	min=min(index[,c(m)])
	x = index[,c("group",m)]
	y = x %>% group_by(group) %>% summarise_(Max=paste('max(',m,')',sep=""))
	y=as.data.frame(y)
	rownames(y)=y$group
	index$y=y[as.character(index$group),]$Max + (max-min)*0.05
	
if (FALSE){
	write.table(paste("SampleID\t", sep=""), file=paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/alpha_",m,"_raw.txt",sep=""), append = F, quote = F, eol = "", row.names = F, col.names = F)
	suppressWarnings(write.table(index[,c(m,"group")], file=paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/alpha_",m,"_raw.txt",sep=""), append = T, quote = F, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = T, col.names = T))
}

	p = ggplot(index, aes(x=group, y=index[[m]], color=group)) +
		geom_boxplot(alpha=1, outlier.size=0, size=0.7, width=0.5, fill="transparent") +
		labs(x="Groups", y=paste(m, "index")) + theme_classic() + main_theme +
		geom_text(data=index, aes(x=group, y=y, color=group, label= stat)) +
		geom_jitter( position=position_jitter(0.17), size=1, alpha=0.7)
	if (length(unique(sub_design$group))>3){
		p=p+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))
	}
color = c("#00BFC4", "#F9766E", "#9E7C61", "#00BFC4", "#F9766E", "#9E7C61")
  p = p + scale_color_manual(values = color)
  # p = p + geom_violin()
	# p
	# ggsave(paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1subspecies/alpha_", m, ".pdf", sep=""), p, width = 5, height = 3)
	p
# }
```

## 1.F Stackplot show taxonomy composition in Phylum level

(F) Phylum-level distribution of the indica and japonica root microbiome in two fields. The differences in the root microbiome between indica and japonica were detectable at the phylum level. Major differences were detected in both fields. Acidobacteria, Bacteroidetes, Spirochaetes, Chloroflexi, Ignavibacteriae, Nitrospirae, and Verrucomicrobia show higher relative abundance in indica than japonica, while the relative abundance of Alphaproteobacteria is higher in japonica (P < 0.001). The number of biological replicates is as follows: in field I, indica (n = 201), japonica (n = 80); in field II, indica (n = 201), japonica (n = 81).


```{r taxonomy, echo=TRUE}
site="https://mirrors.tuna.tsinghua.edu.cn/CRAN"
# Delect dependency, install or loading packages
package_list = c("reshape2","ggplot2","vegan")
# Check each packages is available
for(p in package_list){
	if(!suppressWarnings(suppressMessages(require(p, character.only = TRUE, quietly = TRUE, warn.conflicts = FALSE)))){
		install.packages(p, repos=site)
		suppressWarnings(suppressMessages(library(p, character.only = TRUE, quietly = TRUE, warn.conflicts = FALSE)))
  }
}

# Read input file
# Design file
design = read.table("/mnt/bai/yongxin/rice/xianGeng/doc/design.txt", header=T, row.names=1, sep="\t")
# Group by
design$group = design$groupID

# Select by manual set group
if (TRUE){
	sub_design = subset(design, group %in% c("LTEJ","LIND","LSoil1","HTEJ","HIND","HSoil1"))
# Set group order
	sub_design$group  = factor(sub_design$group, levels=c("LTEJ","LIND","LSoil1","HTEJ","HIND","HSoil1"))
}else{
	sub_design = design[,c("SampleID","group")]
}

# Draw figure in phylum level and Proteobacteria class

m = method = c("pc")
# for(m in method){
	# read usearch taxonomy summary file
	tax_sample = read.table(paste("/mnt/bai/yongxin/rice/xianGeng/result/tax/sum_", m, ".txt", sep=""), header=T, row.names=1, sep="\t", comment.char="") 

	# Decreased sort by abundance
	mean_sort = tax_sample[(order(-rowSums(tax_sample))), ]
	mean_sort = as.data.frame(mean_sort)
	# Filter Top 9 , and other group into Low abundance
	other = colSums(mean_sort[10:dim(mean_sort)[1], ])
	mean_sort = mean_sort[1:(10 - 1), ]
	mean_sort = rbind(mean_sort,other)
	rownames(mean_sort)[10] = c("Low abundance")
	# Double check
	# colSums(mean_sort)

	# Cross filter metadata and features table
	idx = rownames(sub_design) %in% colnames(mean_sort)
	sub_design=sub_design[idx,]
	mean_sort = mean_sort[,rownames(sub_design)]


	# 4.1 Stackplot for each samples
	merge_tax=mean_sort
	write.table("\t", file=paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/tax_pc_", m, "_sample.txt",sep=""),append = F, quote = F, eol = "", row.names = F, col.names = F)
	suppressWarnings(write.table(merge_tax, file=paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/tax_pc_", m, "_sample.txt",sep=""), append = T, quote = F, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = T, col.names = T))

	# Select group information
	sampFile = data.frame(sample=row.names(sub_design), group=sub_design$group,row.names = row.names(sub_design))

	# Add taxonomy
	mean_sort$tax = rownames(mean_sort)
	data_all = as.data.frame(melt(mean_sort, id.vars=c("tax")))
	# Set taxonomy order by abundance, default by alphabet
	if (FALSE){
		data_all$tax  = factor(data_all$tax, levels=rownames(mean_sort))
	}
	data_all = merge(data_all, sampFile, by.x="variable", by.y = "sample")

	p = ggplot(data_all, aes(x=variable, y = value, fill = tax )) + 
		geom_bar(stat = "identity",position="fill", width=1)+ 
		scale_y_continuous(labels = scales::percent) + 
		facet_grid( ~ group, scales = "free_x", switch = "x") +  theme(strip.background = element_blank())+
		theme(axis.ticks.x = element_blank(), axis.text.x = element_blank())+
		xlab("Groups")+ylab("Percentage (%)")+ theme_classic()+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))
	p
	# Saving figure in PDF/PNG for editing and viewing.
	# ggsave(paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/tax_pc_", m, "_sample.pdf", sep=""), p, width = 5, height = 3)
	# ggsave(paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/tax_pc_", m, "_sample.png", sep=""), p, width = 5, height = 3)
	# print(paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/tax_pc_", m, "_sample.pdf/png/txt finished.", sep = ""))


	# 4.2 Group average stackplot

	# Calculate average relative abundance for each group
	mat_t = t(merge_tax)
	mat_t2 = merge(sampFile, mat_t, by="row.names")
	mat_t2 = mat_t2[,c(-1,-2)]
	mat_mean = aggregate(mat_t2[,-1], by=mat_t2[1], FUN=mean) # mean
	mat_mean_final = do.call(rbind, mat_mean)[-1,]
	geno = mat_mean$group
	colnames(mat_mean_final) = geno

	mean_sort=as.data.frame(mat_mean_final)
	write.table("\t", file=paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/tax_pc_", m, "_group.txt",sep=""),append = F, quote = F, eol = "", row.names = F, col.names = F)
	suppressWarnings(write.table(merge_tax, file=paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/tax_pc_", m, "_group.txt",sep=""), append = T, quote = F, sep="\t", eol = "\n", na = "NA", dec = ".", row.names = T, col.names = T))

	# data melt for ggplot2
	mean_sort$tax = rownames(mean_sort)
	data_all = as.data.frame(melt(mean_sort, id.vars=c("tax")))
	# Set taxonomy order by abundance, default by alphabet
	if (FALSE){
		data_all$tax  = factor(data_all$tax, levels=rownames(mean_sort))
	}

	p = ggplot(data_all, aes(x=variable, y = value, fill = tax )) + 
	  geom_bar(stat = "identity",position="fill", width=0.7)+ 
	  scale_y_continuous(labels = scales::percent) + 
	  xlab("Groups")+ylab("Percentage (%)")+ theme_classic()
	if (length(unique(data_all$variable))>3){
		p=p+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))
	}
	# library(RColorBrewer) # https://book.2cto.com/201408/45552.html
	# display.brewer.all(type = "qual") # set discrete color
  # p+ scale_fill_manual(values = brewer.pal(10, "Set3"))
	p
	# Saving figure in PDF/PNG for editing and viewing.
	# ggsave(paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1subspecies/tax_pc_", m, "_group.pdf", sep=""), p, width = 5, height = 3)
	# ggsave(paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/tax_pc_", m, "_group.png", sep=""), p, width = 5, height = 3)
	# print(paste("/mnt/bai/yongxin/rice/xianGeng/fig1/1/tax_pc_", m, "_group.pdf/txt finished.", sep = ""))

# }


```



